# Data transformation

**1. Revenue by Geographical Area**
<br>
Eliminated total and subtotal revenue of area and kept all revenues value of smallest region unit in numeric type. And converted wide data to long data by using `tidyverse` package. After preprocessing all quarters' data, we concatenated all quarters' data with each quarter specified.
```{r}
clean_geo <- function(path, quarter){
  library(tibble)
  library(tidyr)
  library(dplyr)
  library(data.table)
  table = read.csv(file = path)

  colnames(table)[2] = "Country"
  colnames(table)[3] = "2020"
  colnames(table)[4] = "2019"

  table<-table[!(table$Country %like% "TOTAL" | table$Country %like% "Total"),]
  table$`2020` = as.numeric(gsub(",", "", table$`2020`
                                 ))
  table$`2019` = as.numeric(table$`2019`)
  table = table[2:4]
  table <-table %>%  pivot_longer(cols = !Country, names_to = "Year", values_to = "Revenue") 
  table['Quarter'] = quarter
  table["Region"] = NA
  table$Region[table$Country %like% "France"] = "Europe"
  table$Region[table$Country %like% "Japan"] = "Asia"
  table$Region[table$Country %like% "Americas"] = "Americas"
  table$Region[table$Country %like% "Other"] = "Other"
 
   return(table)
}

geo_Q1 = clean_geo('rawdata/2020_Q1_Rev_Geo.csv', 'Q1')
geo_Q2 = clean_geo('rawdata/2020_Q2_Rev_Geo.csv', 'Q2')
geo_Q3 = clean_geo('rawdata/2020_Q3_Rev_Geo.csv', 'Q3')
geo_Q4 = clean_geo('rawdata/2020_Q4_Rev_Geo.csv', 'Q4')
geo = rbind(geo_Q1, geo_Q2, geo_Q3, geo_Q4)
write.csv(geo,"cleaneddata/rev_by_geo_quarterly_2020.csv")
```


**2. Store Allocation**
<br>
To be compatible with the region name in the `maps` package, we converted the country names of United Kingdoms and Principality of Monaco to their abbreviation. And we also included the Caribbean in Americas, Hong Kong and Macao in China to match the boundary in packages. 
```{r}
store <- read.csv("rawdata/Storeinfo.csv")[,-1]
store$Country[4] <- "UK"
store$Country[7] <- "Monaco"
China <- store %>% 
  filter(Country == "Hong Kong" | Country == "Macao" | Country == "Mainland China")
Americas <- store %>% 
  filter(Country == "Caribbean" | Country == "United States")
Americas <- c("USA", sum(Americas$number.of.stores), sum(Americas$new))

China <- c("China", sum(China$number.of.stores), sum(China$new))
store <- store %>% 
  mutate(number.of.stores = as.numeric(number.of.stores)) %>% 
  mutate(new = as.numeric(new)) %>% 
  filter(Country != "Hong Kong" & Country != "Macao" & Country != "Mainland China" & Country != "United States" & Country != "Caribbean") %>% 
  rbind(China) %>% 
  rbind(Americas) %>% 
  mutate(number.of.stores = as.integer(number.of.stores)) %>% 
  mutate(new = as.integer(new))
write.csv(store,"cleaneddata/storeinfo.csv")

```


**3. Revenue by Sector**
<br>
Converted all revenue to numeric type and eliminated total and subtotal revenue of sectors. Also renamed sectors' name by eliminating footnotes. Then we converted wide data to long data by using `tidyverse` package. After preprocessing all quarters' data, we concatenated all quarters' data with each quarter specified. 
```{r}
clean_sec<- function(path, quarter){
  library(tibble)
  library(tidyr)
  library(dplyr)
  library(data.table)
  table = read.csv(file = path)

  colnames(table)[2] = "Sector"
  colnames(table)[3] = "2020"
  colnames(table)[4] = "2019"
  table$`Sector` = gsub('[[:digit:]]+', '', table$`Sector`)
  table$`2020` = as.numeric(gsub(",", "", table$`2020`
                                 ))
  table$`Sector`[table$`Sector` %like% "sectors"] = "Other Hermes sectors"
  table$`2019` = as.numeric(table$`2019`)
  table<-table[!(table$Sector %like% "TOTAL" ),]
 
  table = table[2:4]
  table <-table %>%  pivot_longer(cols = !Sector, names_to = "Year", values_to = "Revenue") 
  table['Quarter'] = quarter

 
   return(table)
}

sec_Q1 = clean_sec('rawdata/2020_Q1_Rev_Sector.csv', 'Q1')
sec_Q2 = clean_sec('rawdata/2020_Q2_Rev_Sector.csv', 'Q2')
sec_Q3 = clean_sec('rawdata/2020_Q3_Rev_Sector.csv', 'Q3')
sec_Q4 = clean_sec('rawdata/2020_Q4_Rev_Sector.csv', 'Q4')

sec = rbind(sec_Q1, sec_Q2, sec_Q3, sec_Q4)
write.csv(sec,"cleaneddata/rev_by_sector_quarterly_2020.csv")
```

**4. Key Figures**
<br>
First, we selected important variables that we want to discuss in key figures. Then we transferred the rownames into date column. Since these metrics all have different units, and it would be meaningless to put them together in one plot, we decided to transfer all values into index in a way it can provide a better comparison.
```{r}
key_figures.1620<-read.csv("rawdata/2016_2020_key_figures.csv")
table<-key_figures.1620%>%filter(Category%in%c('Revenue','Workforce -number of employees','Recurring operating income 2'))
df<-as.data.frame(t(table))[-c(1:2),]
colnames(df)<-c('Revenue','RecurringOI','Workforce')
date<-rownames(df)
rownames(df)<-NULL
df['Year']<-date
df1<-df%>%mutate(Revenue=as.numeric(Revenue),Workforce=as.numeric(Workforce),RecurringOI=as.numeric(RecurringOI))
index<-function(y){
  standard<-y[1]
  a<-lapply(y, function(x) (x/standard)*100)
  return(unlist(a))
}
df2<-df1%>% mutate_at(c("Revenue",'RecurringOI', "Workforce"), ~(index(.) %>% as.vector))
df3<-df2%>%pivot_longer(c('Revenue','RecurringOI','Workforce'),names_to='Category',values_to='value')%>%mutate(Category=as.factor(Category))
df3['Year']<-df3$Year%>%str_remove('\\X')
write.csv(df3,"cleaneddata/keyfigures2016_2020.csv")
```

**5. 2019 & 2020 Financial Statements**
<br>
For income statements, we extracted the expenses, income, and final net profits. Since we would like to show the flow of revenue and compare the final profit between 2020 and 2019, we eliminated the intermediate incomes. We also converted income and expenses to their abbreviation so that they could fit x-axis better in the waterfall plot.
<br> 
For balance Sheets, we combined the asset data as well as the liability data together from 2018 to 2020. Then we included the major terms in balance sheet and merged the assets with liabilities. We transformed the dataframe into a better form for plotting and removed the ',' inside amount column so that we could easily transfer the data type from character to numeric.
```{r}
library(stringr)
clean_income_statement<- function(incomestatement){
  incomestatement <- incomestatement[1:15,]
  colnames(incomestatement)[2] = 'statement'
  incomestatement[,2] <- gsub('\\(|\\)|\\,','',incomestatement[,2])
  incomestatement[,2] = as.numeric(incomestatement[,2])
  incomestatement[c(2,4,5,9,11,14),2] = incomestatement[c(2,4,5,9,11,14),2] *(-1)
  incomestatement$Measure = c("relative", "relative","total", "relative", "relative","total", "relative", "total", "relative", "total", "relative","relative", "total","relative","total")
  incomestatement = incomestatement[-c(3,6, 8, 10, 13), ]
  incomestatement$Category = c("Revenue", "Cost of Sales", "S&A expenses", "Other I&E", "Other non-recurring I&E", "Net financial income", "Income tax", "Net income from associate", "Non-controlling interests", "Net Income")

return(incomestatement)

}

incomestatement <- read.csv("rawdata/2020_income_statementr.csv")[-1]

incomestatement19 <- clean_income_statement(incomestatement[,c(1,3)])
incomestatement20 <- clean_income_statement(incomestatement[,c(1,2)])
write.csv(incomestatement19,"cleaneddata/incomestatement19.csv")
write.csv(incomestatement20,"cleaneddata/incomestatement20.csv")

```
```{r}
asset20<-read.csv('rawdata/2020_balance_sheet_asset.csv')
asset19<-read.csv('rawdata/2019_balance_sheet_asset.csv')
liab20<-read.csv('rawdata/2020_balance_sheet_liability.csv')
liab19<-read.csv('rawdata/2019_balance_sheet_liability.csv')
asset<-merge(asset19,asset20,by='category')
liability<-merge(liab19,liab20,by='category')
asset<-asset%>%select(category,X31.12.2018.restated,X31.12.2019.y,X31.12.2020)%>%filter(category%in%c('Current assets','Non-current assets'))
liability<-liability%>%select(category,X31.12.2018.restated,X31.12.2019.y,X31.12.2020)%>%filter(category%in%c('Equity','Current liabilities','Non-current liabilities'))
liability['category']<-c('Current liabilities','Stockholder Equity','Non-current liabilities')
colnames(asset)<-c('Category','2018','2019','2020')
colnames(liability)<-c('Category','2018','2019','2020')
asset['al']<-rep('asset',dim(asset)[1])
liability['al']<-rep('liability',dim(liability)[1])
balance<-rbind(asset,liability)
balancesheets<-balance%>%pivot_longer(c('2018','2019','2020'),names_to='Year',values_to='amount')%>%mutate(al=as.factor(al),Year=as.factor(Year))
value<-balancesheets$amount
value<-value%>%str_replace("\\,",'')
balancesheets['amount']<-as.double(value)
balancesheets<-balancesheets%>%mutate(amount=as.numeric(amount))
write.csv(balancesheets,"cleaneddata/balancesheet.csv")
```
 

**6. Stock Information**
<br>
Converted the Date column into Date data type. Joined all different stocks data together so that we could calculate the return rate by calculaing the differences of prices between $Day_t$ and $Day_{t+1}$ and dividing the differences by $Price_t$(We assumed the first day return to be 0).
```{r}
cac40i<-read.csv("rawdata/CAC40_stock_info.csv")
hstockprice<-read.csv("rawdata/Hermes_stock_info.csv")
lvstockprice<-read.csv("rawdata/LVMH_stock_info.csv")
sp500price<-read.csv("rawdata/S&P500_info.csv")
kerstockprice<-read.csv("rawdata/KERING_stock_info.csv")
library(lubridate)
hstock <-hstockprice%>%mutate(date=ymd(date))%>%select(date,RMS.PA.Close)
lvstock <- lvstockprice%>%mutate(date=ymd(date))%>%select(date,MC.PA.Close)
sp500<-sp500price%>%mutate(GSPC.Close=as.numeric(GSPC.Close))%>%mutate(date=ymd(date))%>%select(date,GSPC.Close)
kerstock <- kerstockprice%>%mutate(date=ymd(date))%>%select(date,KER.PA.Close)
cac<-cac40i%>%mutate(date=ymd(date))%>%select(date,FCHI.Close)
lux<-inner_join(hstock,lvstock)%>%inner_join(kerstock)
closeprice<-inner_join(lux,sp500)%>%inner_join(cac)
return<-closeprice
for (i in 2:6){
  for (j in 1:dim(closeprice)[1]){
    if (j==1){
      return[j,i]<-0
    }else{
      return[j,i]<-(closeprice[j,i]-(closeprice[j-1,i]))/closeprice[j-1,i]
    }
  }
}
colnames(return)<-c('Date','HERMES','LVMH','KERING','S&P500',"CAC40")
write.csv(return,"cleaneddata/stockreturn.csv")
```



**7. 2010-2020 Revenue vy Geographical Area(d3 data)**

Introduced Year column as rownames and use it for d3 graph.

```{r}
data <- read.csv(file = "rawdata/2010_to_2020_Rev_Geo.csv",skip = 2)
data <- data[,-1] %>% 
  column_to_rownames("NA.")
write.csv(data,"cleaneddata/d3data.csv")
```



